---
title: "Eating Out"
author: "Mikaela M. Elias"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "`r Sys.Date()`"    
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## There were two years in which the General Social Survey asked about the frequency of eating out. The variable name you are looking for is "eatout".
### Find those years and for the first year the question was asked download that years data in a stata format - its name will be "GSSxxxx.dta" where the xxxx is replaced by the year.  For example if the year was 1983 its name would be GSS1983.dta. Your assignment is to download the GSS yearly dataset for the first year the question was asked and then  write up the answer to the question by editing the  code block in line 31 to eval=TRUE and finish the job. 

$H_0$ There is no difference among the various races with frequency of eating out  
$H_A$ There is a statistical difference between at least two races with the frequency of eating out  


```{r include=FALSE,echo=FALSE}
source(file="fisherXY.R")
require(tidyverse)
require(tigerstats)
require(haven)
require(knitr)
require(foreign)
library(haven)
library(plyr)
```

```{r, eval=TRUE, WARNING=FALSE}

GSS <-read_dta(file="GSS1998.dta")
GSS <- droplevels(GSS)
mydata <- select(GSS,race,age,eatout)
mydata <- na.omit(mydata)
```


# Methods
$H_0$ There is no difference among the various races with frequency of eating out  
$H_A$ There is a statistical difference between at least two races with the frequency of eating out  
         
race~eatout          
is categorical~categorical          
We will use the helper file CAT~CAT
          
           
# Graphical Descriptive 
          
```{r}
#mydata$race=revalue(mydata,$race=c("white","black","other")
barchartGC(~race + eatout,data=mydata)
barchartGC(~race + eatout,data=mydata, type="percent")
```
         
The races are white, black, other. The blue represents those who ate out last week, and the orange represents those who did not. White individuals eat out more than any of the other races. 

         
# Numerical Results
         
```{r}
table1 <- xtabs(~race + eatout, data=mydata)
rowPerc(table1)
colPerc(table1)
```
         
The Numerical results show that white individuals eat out 83.11% more than the other races at least one time a week, and 16.89% didin't. 
        
    
# Inferential results 
         
```{r}
chisq.test(table1)
chisqtestGC(table1)
fisherXY(mydata$race,mydata$eatout,printAll= T)
```
         
The chi-squared test shows a p-value is 0.000002287, which is less than the acceptable p-value of 0.05, so we will reject the null hypothesis. This means there is a statistical difference between at least 2 races when eating out.            
The FisherXY test results show the p-value 0.00001183, which is less than the acceptable p-value of 0.05, so we will reject the null hypothesis.This means there is a difference between white and black individuals when eating out.        
The FisherXy test results shows the p-value 0.0072, which is less than the acceptable p-value of 0.05, so we will rejects the null hypothesis. This means there is a difference between white and other individuals when eating out.          
The FisherXY test results shows the p-value of 0.5993, which is more than the acceptable p-value of  0.05, so we will fail to reject the null hypothesis. This means there is no difference between the races when eating out. 



         
# Conclusion 



